---
title: "COMPSCIX 415.2 Homework 4"
author: "Dai_Zhechen"
date: "2/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library(nycflights13)
```
##Exercises 5.6.7
###(2)

```{r}
not_cancelled <-
  flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))
```
```{r}
not_cancelled %>% count(dest)
```
####without using `count()`
```{r}
not_cancelled %>%
  group_by(dest) %>%
  summarise(n = n())
```
```{r}
not_cancelled %>% count(tailnum, wt = distance)
```
####without using `count()`
```{r}
not_cancelled %>%
  group_by(tailnum) %>%
  summarize(n = sum(distance))
```

###(4)
```{r}
flights %>%
  group_by(day) %>%
  summarise(cancelled = mean(is.na(dep_delay)),
            mean_dep = mean(dep_delay, na.rm = T),
            mean_arr = mean(arr_delay, na.rm = T)) %>%
  ggplot(aes(y = cancelled)) +
  geom_point(aes(x = mean_dep), colour = "red") +
  geom_point(aes(x = mean_arr), colour = "blue") +
  labs(x = "Avg delay per day", y = "Cancelled flights per day")
```

It looks like they have the positive relationship with each other, the higher the average delay per day, the higher the cancelled flights per day.

###(6)
You can use the `sort` to sort the cases based on the `count()`.

###(5) Extra Credit
1.
```{r}
flights %>%
  group_by(carrier) %>%
  summarise(dep_max = max(dep_delay, na.rm = T),
            arr_max = max(arr_delay, na.rm = T)) %>%
  arrange(desc(dep_max, arr_max)) %>%
  filter(1:n() == 1)
```


Carrier `HA`

##Exercises 10.5
###(1)
```{r}
data("mtcars")
class(mtcars)

mtcars <- as_tibble(mtcars)
class(mtcars)
```

Get the `class()` of object and see whether it has `tbl_df` and `tbl`.

###(2)
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

```{r}
df <- as_tibble(data.frame(abc = 1, xyz = "a"))
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

In some cases, a data frame will returns a different thing.

Tibble will return the same thing, providing consistency.

###(3)
```{r}
var <- "mpg"
as_tibble(mtcars)[[var]]
```

###(6)
`options(tibble.width = Inf)` for all columns to be printed (Confused)

##Exercises 12.3.3
###(2)
```{r}
table4a %>% 
  gather("1999", "2000", key = "year", value = "cases")
```

Because `gather()` can not find the columns' name

###(3)
```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)
```
```{r}
people %>%
  mutate(unique_id = c(1, 2, 2, 3, 3)) %>%
  select(unique_id, everything()) %>%
  spread(key, value)
```

Phillip Woods has two columns of age, it is inpossible for one person, we need to unique them.

###(4)
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
```

Gather it.
```{r}
preg %>%
  gather(gender, values, -pregnant)
```

##Exercises 12.4.3
###(1)
`extra` If sep is a character vector, this controls what happens when there are too many pieces. There are three valid options:

"warn" (the default): emit a warning and drop extra values.

"drop": drop any extra values without a warning.

"merge": only splits at most length(into) times

`fill` If sep is a character vector, this controls what happens when there are not enough pieces. There are three valid options:

"warn" (the default): emit a warning and fill from the right

"right": fill with missing values on the right

"left": fill with missing values on the left

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "warn")
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop")
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "merge")
```
```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three", "four"))
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three", "four"), fill = "warn")
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three", "four"), fill = "right")
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three", "four"), fill = "left")
```

###(2)
`unite()` `remove`	If TRUE, remove input columns from output data frame.

`separate()` `remove`	If TRUE, remove input column from output data frame.

Allows you to remove the original columns that you unite/separate on.You might want to leave them as they are if you're checking whether the transformation was done correctly.

##Answer these questions:
###1.
```{r}
library(tidyverse)
file_path <- '/Users/jerryd/Desktop/JERRYGit/Lab4files/baby_names.txt'
txt_data <- read.delim2(file = '/Users/jerryd/Desktop/JERRYGit/Lab4files/baby_names.txt', sep = "|")
```
```{r}
glimpse(txt_data)
```
```{r}
write_csv(txt_data, path = '/Users/jerryd/Desktop/JERRYGit/Lab4files/baby_names.csv')
```
```{r}
file_path <- '/Users/jerryd/Desktop/JERRYGit/Lab4files/baby_names.csv'
csv_data <- read_csv(file = '/Users/jerryd/Desktop/JERRYGit/Lab4files/baby_names.csv')
```
```{r}
glimpse(csv_data)
```
 test 
